---
title: "R Markdown in action"
subtitle: "Using ioslides"
author: Josselin Noirel
date: Feb 2020
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, comment=NULL)
library("DT")
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with bullets | Navigation

* 'f': enable fullscreen mode
* 'w': toggle widescreen mode
* 'o': enable overview mode
* 'h': enable code highlight mode
* 'p': show presenter notes

## Slide with R output

```{r cars, echo = TRUE}
datatable(cars)
```

## Slide with code | and a subtitle

```python
import numpy as np
π = np.pi

x = np.linspace(0, 2 * π)
y = np.exp(x)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

