---
title: "R Markdown in action"
subtitle: "Using Slidy"
author: Josselin Noirel
date: Feb 2020
output:
  slidy_presentation:
    footer: "Copyright statement"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, comment=NULL)
library("DT")
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with bullets

* 'C': Show table of contents (the right sub-figure in Figure 4.2 has shown the table of contents).
* 'F': Toggles the display of the footer.
* 'A': Toggles display of current vs all slides (useful for printing handouts).
* 'S': Make fonts smaller.
* 'B': Make fonts larger.

## Slide with R output

```{r cars, echo = TRUE}
datatable(cars)
```

## Slide with code

```python
import numpy as np
π = np.pi

x = np.linspace(0, 2 * π)
y = np.exp(x)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

