---
title: "Presentation Ninja"
subtitle: "with xaringan"
author: "Josselin Noirel"
institute: "CNAM"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    yolo: true
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version=FALSE)
library("DT")
```

# What is cool about xaringan

Use the Ninja presentation template.

You can easily produce incremental slides using `--` as a separator

--

* This is an example
* Another slide

New slides can be started with a `# Section`

---

Or using a `---` separator!

# Hello Ninja

As a presentation ninja, you certainly should not be satisfied by the "Hello World" example. You need to understand more about two things:

1. The [remark.js](https://remarkjs.com) library;

1. The **xaringan** package;

Basically **xaringan** injected the chakra of R Markdown (minus Pandoc) into **remark.js**. The slides are rendered by remark.js in the web browser, and the Markdown source needed by remark.js is generated from R Markdown (**knitr**).

---

# remark.js

You can see an introduction of remark.js from [its homepage](https://remarkjs.com). You should read the [remark.js Wiki](https://github.com/gnab/remark/wiki) at least once to know how to

- create a new slide (Markdown syntax<sup>*</sup> and slide properties);

- format a slide (e.g. text alignment);

- configure the slideshow;

- and use the presentation (keyboard shortcuts).

It is important to be familiar with remark.js before you can understand the options in **xaringan**.

.footnote[[*] It is different with Pandoc's Markdown! It is limited but should be enough for presentation purposes. Come on... You do not need a slide for the Table of Contents! Well, the Markdown support in remark.js [may be improved](https://github.com/gnab/remark/issues/142) in the future.]

---

# Slide with R output

```{r cars, echo = TRUE}
datatable(cars)
```

---

# Slide with code

```python
import numpy as np
π = np.pi

x = np.linspace(0, 2 * π)
y = np.exp(x)
```

---

# Slide with Plot

```{r pressure}
plot(pressure)
```
